--- 
title: "Sticky Pi, a high-frequency smart insect trap to study daily activity in the field"
author: "Quentin Geissmann"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: 
  bookdown::gitbook:
    includes:
       in_header: ga-script.html
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: sticky-pi/sticky-pi.github.io
description: "This is the documentation for the Sticky Pi project, a system to study insect activity in the field."
---
```{r include=FALSE, cache=FALSE}
options("datatable.print.nrows" = 30)
```

```{r, echo=FALSE}
options("datatable.print.nrows" = 30)
```

# Introduction{-}


TODO description of the project 

<!--chapter:end:index.Rmd-->

```{r include=FALSE, cache=FALSE}
options("datatable.print.nrows" = 30)
```
# Overview{#overview -}

## Scientific Context
## Sticky Pi Devices
## Platform
## Machine Learning

<!--chapter:end:01-intro.Rmd-->

```{r include=FALSE, cache=FALSE}
options("datatable.print.nrows" = 30)
```
# Issues and community {#community -}

## Citation{-}

`retomics` is an academic software. As such, it is -- and will always be -- completely free and open source. 
**If you use rethomics as part of your research, please cite [our reference publication](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0209331).**

## Having troubles{-}

If you are having issues or you want help with something, the best thing you can do is **fill an "issue" on the github repository** of the relevant package.
For instance, if you are struggling to load DAMS data, you should go to the [the damr package](https://github.com/rethomics/damr/issues).
This way, you can see if other users have had the same issue, and if we are already working on it!

## Contributing {-}

We welcome external contributions and hope rethomics develops as a community.
There are several ways you can contribute:

* By requesting features and reporting bugs through the github issue system
* By sending pull requests to preexisting packages
* By volunteering to develop a new package (for instance to import a new type of data)


<!--chapter:end:99-contact.Rmd-->

